Nodal Discontinuous Galerkin Method for the Euler Equations in GR

### 2018-11-06 Documents/Euler/dgEulerGR.tex
Changed representation of cell-average from overline to subscript K

>>>>

\subsection{Demanding that $q>0$}

Sometimes it happens that the cell-average of $q$, $q_{K}\equiv q\left(\bU_{K}\right)<0$, so our positivity limiter will fail. To get around this we modify the conserved energy, $\tau$, to demand that $q=\ve$, where $0<\ve\ll1$. The transformation we make is:
\begin{equation}
   \tau_{K}\longrightarrow\alpha\,\tau_{K},\hspace{1em}\alpha>1.
\end{equation}
This modifies the definition of $q_{K}$ from:
\begin{equation}
   q_{K}=\tau_{K}+D_{K}-\sqrt{D_{K}^{2}+S_{K}^{2}+\ve}<0,
\end{equation}
to:
\begin{equation}
   \ve=\alpha\,\tau_{K}+D_{K}-\sqrt{D_{K}^{2}+S_{K}^{2}+\ve}.
\end{equation}
Solving this for $\alpha$, we get:
\begin{equation}
   \alpha=\tau_{K}^{-1}\left[\ve-D_{K}+\sqrt{D_{K}^{2}+S_{K}^{2}+\ve}\right].
\end{equation}
